\documentclass[12pt]{article}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyfoot{}
\rhead{\thepage}
\renewcommand{\headrulewidth}{0pt}
\pagenumbering{arabic}

\begin{document}
% #region What are you applying for
   
    Hello,
    \par I'm writing to you to inquire about your advertised A2 position in your sound department.
    This job stood out to me due to the location and included housing. I've never been to Maine but have always heard it's quite nice.
% #endregion
%  #region Why you are good for the job
    \par When it comes to the qualifications for this listing, I have been mixing for musicals of varying size for 5 years, acting as both A1 and A2.
    I also have extensive experience in paperwork preparation, creating multiple spreadsheets for each show I have worked on. 
    For many of the shows I have worked on, I have created bespoke sound effects, as well as creating longer versions of instrumentals through writing new orchestrations.
    My experience ranges from tiny high school musicals to large community theatre shows, as well as working as a house technician for a college. This range of work helps informs my designs in many ways.
% #endregion 
% #region Something about the company
    \par When it comes to companies I look for work from, more community based companies are definitely a plus. One of the first theatre companies I worked for was a historic theatre company in North Carolina.
    Having worked for said company, I have such a strong appreciation for companies with a strong connection to their communities. Looking at the values of Maine State, it seems like this holds true.
% #endregion
% #region Summary
    \par All in all, thanks for reading this letter, I look forward to talking to you in the future.\\
    Sincerely,
\end{document}