\documentclass[12pt]{article}
\usepackage[letterpaper, portrait, margin=1in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage[T1]{fontenc}
\usepackage{mathptmx}
\usepackage[backend=biber, style=mla]{biblatex}
\pagestyle{fancy}
\addbibresource{cga.bib}    

\fancyhf{} % sets both header and footer to nothing}
\renewcommand{\headrulewidth}{0pt}
\pagenumbering{arabic}
\rhead{Sheehan \thepage} 
\fancypagestyle{1stPage}{
    \fancyhf{}
    \renewcommand{\headrulewidth}{0pt} % removes horizontal header line
    \lhead{Owen Sheehan \\ Tina Cafaso \\ Interpretation and Argument \\ 9/29/23}
    \rhead{ Sheehan 1}
}

\thispagestyle{1stPage}

\begin{document}
    \begin{doublespace}

        \begin{center}
            \vspace*{6pt}
            Comparative Genre Analysis
        \end{center}

    \vspace{-18pt}
    \par%Intro Paragraph
        The articles ``I tweet honestly, I tweet passionately: Twitter users, context collapse, and the imagined audience'' as well as ``How Real Are You on Facebook''
        both deal with a users authenticity online. Where ``I tweet honestly'' is written for an academic audience, ``How Real Are You on Facebook'' is more intended for a wide audience.
        While they both share the same ideas about authenticity, the use of tone, format, and sourcing are quite different, albeit with the occasional slight similarity. 
    \par%1st supporting
        The first major difference between the two artic;es is how they approach citations. In ``How Real Are You on Facebook'', it's charitable to say that author Sophie Goodman uses citations.
        However unlike most cases of online articles not using sources, at least anecdotely, this seems more of a choice of readability, rather than a way to control access to information.
        One way we can be sure of this is that she does mention the authors that she is paraphrasing. Another point of interest is that she does link to academic journals in three places.
        The first two instances come from linking to ``I tweet honestly'' where Goodman introduces language that is explained in said article,
        ``The ethnographer danah boyd \dots, one of the earliest researchers of social lives online,
        refers to ``\underline{\href{http://con.sagepub.com/content/14/1/13.short?rss=1&ssource=mfr}{social convergence}}'' in social networking sites. Social convergence, she argues, occurs when multiple social worlds merge.
        This results in ``\underline{\href{http://nms.sagepub.com/content/13/1/114}{context collapse}},'' meaning social media sites bring together different social contexts simultaneously'' \autocite{facebook}. 
        The underlined words link to ``I tweet honestly'', and are therefor, in a sense, are a type of citation. However, unlike actual citations, it fails to give more information on where in the text this definition comes from, 
        making it a lot harder to parse the data.
        The third instance of a academic article being linked comes from a link to ``The Rules of Facebook friendship''\footfullcite{face_friends}. 
        Marwick and boyd, on the other hand, use citations extensively as one would expect from a academic journal, take for example the following quote,
        ``Self-conscious identity performances have been analyzed in internet spaces like social network sites (boyd, 2007; Livingstone, 2005), blogs (Hodkinson and Lincoln, 2008; Reed, 2005), 
        dating sites (Ellison et al., 2006) and personal homepages (Papacharissi, 2002; Schau and Gilly, 2003)'' \autocite[115]{tweet}.
        I think this snippet perfectly outlines the differences in how these two articles cite sources. In Marwick and boyd's article, we see that every time they slightly mention a separate source there is a citation, whereas Goodman just alludes to it.
    \par%2nd supporting
    \par%3rd supporting
    \par%conclusion
    \newpage \printbibliography


    \end{doublespace}
\end{document}
