\documentclass[12pt]{article}
\usepackage[letterpaper, portrait, margin=1in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage[T1]{fontenc}
\usepackage{mathptmx}
\usepackage[backend=biber, style=mla]{biblatex}
\pagestyle{fancy}

% TODO Add Bib
% \addbibresource{placeholder.bib}    

\fancyhf{} % sets both header and footer to nothing}
\renewcommand{\headrulewidth}{0pt}
\pagenumbering{arabic}
\rhead{Sheehan \thepage} 

% TODO Add Variables
\def\class{Technical Management}
\def\prof{Miso Wei}
\def\due{9/16/24}

\fancypagestyle{1stPage}{
    \fancyhf{}
    \renewcommand{\headrulewidth}{0pt} % removes horizontal header line
    \lhead{Owen M. Sheehan \\ \prof{} \\ \class{} \\ \due{}}
    \rhead{ Sheehan 1}
}

\thispagestyle{1stPage}
\begin{document}
\begin{doublespace}
\vspace*{20pt}
 
% #region 
    \par % I have a hard time concentrating when others are speaking
    The first criterion that I put a five down for was ``I have a hard time concentrating on what is being said'', I don't think this is due to a lack of trying however. I historically have had problems relating to ADD, however I no longer am on medical therapy for it since I'm pretty sure I have a slightly different problem that can't be treated with medicine. I do, however try to pay as much attention as I can. I think I can do a bit better in this regard but it would probably be helpful to talk to someone on how to better listen to other people.
    \par % I am uncomfortable or at a loss when the other person expresses emotions
    The second thing that I put a five down for was ``I am uncomfortable or at a loss when the other person expresses emotions'', this also results from the same source as the first criterion. I have huge problems processing both mine and other peoples emotions so I tend to avoid them, not just for my sake but for others as well as well. The thing is when people talk about emotions, I tend to come off as kinda brash since I have a hard time empathizing with other people.
    \par % I keep my feelings to my self
    The last thing that I put a five down for is ``I keep my feelings to my self'', to me this also tracks with the rest of what I have issues with. I think out of all three of the fives, this is what I am ``best'' at, however I have to constantly remind myself to actually express how I feel about things when talking to other people. I tend to withold my feelings in different ways to different people, there are maybe 2 people that I'm actually upfront about my feelings with.
    \par % practical solutions
    I think the best practical solution for all of these is to actively keep in mind all of these things while talking to people, the main reason I struggle with these is because I just don't think about them, I think it's as simple as that. I'm sure there are other things I could do, however I do not think they would be as effective.ssss
\end{doublespace}
\end{document}